---
title: "Blastn300 results"
output:
  html_notebook:
    code_folding: show
    df_print: paged
    fig_retina: 1
    fig_width: 12
    fig_height: 8
    fig_caption: yes
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: no
---

```{css, echo=FALSE}
.scroll-200 {
  max-height: 200px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{css, echo=FALSE}
.tocify .tocify-header {
  #position: fixed;
  #top: 50px;
  #left: 50px;
  width: 350px;
  #height: 400px;
  }
```

```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(reshape2)
  library(Biostrings)
  library(ggpubr)
  })
```

```{r}
rm(list=ls())
gc()
```

# blastn results
## import files
```{r}
blst_mydb = read.table("./blast_db_results/db5.local.out.top")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]

blst_imdb = read.table("./blast_db_results/db5.regional.out.top")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]

blst_global = read.table("./blast_db_results/db5.global.out.top")
blst_global = blst_global[order(blst_global$V1), ]


dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]

temp = inner_join(blst_mydb, blst_imdb, by="V1")
temp2 = inner_join(temp, blst_global, by="V1")
blst_otus = temp2$V1
rm(temp, temp2)

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
# save the global for later comparison with tblastx
saveRDS(blst_global2, "./results_blastn.rds")
```

# statistics
## bitscore median
```{r}
blst_increase_bit = data.frame("V1"=blst_mydb2$V1, "mydb"=blst_mydb2$V12, "imdb"=blst_imdb2$V12, "global"=blst_global2$V12)
data.frame(
  "region" = c("mydb", "imdb", "global"),
  "Median" = round(c(median(blst_increase_bit$mydb), median(blst_increase_bit$imdb), median(blst_increase_bit$global)), 2),
  "Range_bottom" = round(c(range(blst_increase_bit$mydb)[1], 
                    range(blst_increase_bit$imdb)[1], 
                    range(blst_increase_bit$global)[1]), 2),
  "Range_top" = round(c(range(blst_increase_bit$mydb)[2], 
                    range(blst_increase_bit$imdb)[2], 
                    range(blst_increase_bit$global)[2]), 2)
)
```

## pident median
```{r}
blst_increase = data.frame("V1"=blst_mydb2$V1, "mydb"=blst_mydb2$V3, "imdb"=blst_imdb2$V3, "global"=blst_global2$V3)
data.frame(
  "region" = c("mydb", "imdb", "global"),
  "Median" = round(c(median(blst_increase$mydb), median(blst_increase$imdb), median(blst_increase$global)), 2),
  "Range_bottom" = round(c(range(blst_increase$mydb)[1], 
                    range(blst_increase$imdb)[1], 
                    range(blst_increase$global)[1]), 2),
  "Range_top" = round(c(range(blst_increase$mydb)[2], 
                    range(blst_increase$imdb)[2], 
                    range(blst_increase$global)[2]), 2)
)
```

### pident median increment
```{r}
# global - local(mydb)
paste("median global-local", round(median(blst_increase$global) - median(blst_increase$mydb), 2))

# global - regional(imdb)
paste("median global-regional", round(median(blst_increase$global) - median(blst_increase$imdb), 2))

# regional(imdb) - local(mydb)
paste("median regional-local", round(median(blst_increase$imdb) - median(blst_increase$mydb), 2))
```

# statistic2
## Normality
```{r}
# bitscore
ks.test(blst_mydb2$V12, 'pnorm')
ks.test(blst_imdb2$V12, 'pnorm')
ks.test(blst_global2$V12, 'pnorm')
```
**Bitscore values are not normally distributed**

### mydb vs imdb
Is imdb greater than mydb?

#### bit score
```{r}
wilcox.test(blst_imdb2$V12, blst_mydb2$V12, paired = TRUE, alt="greater")
median(blst_imdb2$V12)
median(blst_mydb2$V12)
```

#### Pident
```{r}
# 
wilcox.test(blst_imdb2$V3, blst_mydb2$V3, paired = TRUE, alt="greater")
median(blst_imdb2$V3)
median(blst_mydb$V3)
```
**YES pident & YES bitscore imdb are bigger than mydb**

### mydb vs global
is global greater than mydb?

#### bit score
```{r}
# Bit score
wilcox.test(blst_global2$V12, blst_mydb2$V12, paired = TRUE, alt="greater")
median(blst_global2$V12)
median(blst_mydb$V12)
```

#### Pident
```{r}
wilcox.test(blst_global2$V3, blst_mydb2$V3, paired = TRUE, alt="greater")
median(blst_global2$V3)
median(blst_mydb2$V3)
```
**YES pident & YES bitscore global are bigger than mydb**

### global vs imdb
Is global greater than imdb?

#### bit score
```{r}
wilcox.test(blst_global2$V12, blst_imdb2$V12, paired = TRUE, alt="greater")
median(blst_imdb2$V12)
median(blst_global2$V12)
```

#### Pident
```{r}
wilcox.test(blst_global2$V3, blst_imdb2$V3, paired = TRUE, alt="greater")
median(blst_imdb2$V3)
median(blst_global2$V3)
```
**Yes pident & Yes bitscore global are bigger than imdb**

# blastn finished
```{r}
rm(list=ls())
gc()
```

# tblastx results
## import files
```{r}
blst_mydb = read.table("./blast_db_results/tblastx.db5.local.out.top")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]

blst_imdb = read.table("./blast_db_results/tblastx.db5.regional.out.top")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]

blst_global = read.table("./blast_db_results/tblastx.db5.global.out.top")
blst_global = blst_global[order(blst_global$V1), ]

dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]

temp = inner_join(blst_mydb, blst_imdb, by="V1")
temp2 = inner_join(temp, blst_global, by="V1")
blst_otus = temp2$V1
rm(temp, temp2)

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
# save the global for later comparison with blastn
saveRDS(blst_global2, "./results_tblastx.rds")
```
# statistic
## bitscore median
```{r}
blst_increase_bit = data.frame("V1"=blst_mydb2$V1, "mydb"=blst_mydb2$V12, "imdb"=blst_imdb2$V12, "global"=blst_global2$V12)
data.frame(
  "region" = c("mydb", "imdb", "global"),
  "Median" = round(c(median(blst_increase_bit$mydb), median(blst_increase_bit$imdb), median(blst_increase_bit$global)), 2),
  "Range_bottom" = round(c(range(blst_increase_bit$mydb)[1], 
                    range(blst_increase_bit$imdb)[1], 
                    range(blst_increase_bit$global)[1]), 2),
  "Range_top" = round(c(range(blst_increase_bit$mydb)[2], 
                    range(blst_increase_bit$imdb)[2], 
                    range(blst_increase_bit$global)[2]), 2)
)
```

## pident median
```{r}
blst_increase = data.frame("V1"=blst_mydb2$V1, "mydb"=blst_mydb2$V3, "imdb"=blst_imdb2$V3, "global"=blst_global2$V3)
data.frame(
  "region" = c("mydb", "imdb", "global"),
  "Median" = round(c(median(blst_increase$mydb), median(blst_increase$imdb), median(blst_increase$global)), 2),
  "Range_bottom" = round(c(range(blst_increase$mydb)[1], 
                    range(blst_increase$imdb)[1], 
                    range(blst_increase$global)[1]), 2),
  "Range_top" = round(c(range(blst_increase$mydb)[2], 
                    range(blst_increase$imdb)[2], 
                    range(blst_increase$global)[2]), 2)
)
```

### pident median increment
```{r}
# global - local(mydb)
paste("median global-local", round(median(blst_increase$global) - median(blst_increase$mydb), 2))

# global - regional(imdb)
paste("median global-regional", round(median(blst_increase$global) - median(blst_increase$imdb), 2))

# regional(imdb) - local(mydb)
paste("median regional-local", round(median(blst_increase$imdb) - median(blst_increase$mydb), 2))
```

# statistic2
## Normality
```{r}
# bitscore
ks.test(blst_mydb2$V12, 'pnorm')
ks.test(blst_imdb2$V12, 'pnorm')
ks.test(blst_global2$V12, 'pnorm')
```
**Bitscore values are not normally distributed**

### mydb vs imdb
Is imdb greater than mydb?

#### bit score
```{r}
wilcox.test(blst_imdb2$V12, blst_mydb2$V12, paired = TRUE, alt="greater")
median(blst_imdb2$V12)
median(blst_mydb2$V12)
```

#### Pident
```{r}
wilcox.test(blst_imdb2$V3, blst_mydb2$V3, paired = TRUE, alt="greater")
median(blst_imdb2$V3)
median(blst_mydb$V3)
```
**YES pident & YES bitscore imdb are bigger than mydb**

### mydb vs global
is global greater than mydb

#### bit score
```{r}
wilcox.test(blst_global2$V12, blst_mydb2$V12, paired = TRUE, alt="greater")
median(blst_global2$V12)
median(blst_mydb$V12)
```

#### Pident
```{r}
# Pident
wilcox.test(blst_global2$V3, blst_mydb2$V3, paired = TRUE, alt="greater")
median(blst_global2$V3)
median(blst_mydb2$V3)
```
**YES pident & YES bitscore global are bigger than mydb**

### global vs imdb
Is global greater than imdb

#### bit score
```{r}
median(blst_imdb2$V12)
median(blst_global2$V12)
wilcox.test(blst_global2$V12, blst_imdb2$V12, paired = TRUE, alt="greater")
```

#### Pident
```{r}
# Pident
median(blst_imdb2$V3)
median(blst_global2$V3)
wilcox.test(blst_global2$V3, blst_imdb2$V3, paired = TRUE, alt="greater")
```
**Yes pident & Yes bitscore global are bigger than imdb**

# tblastx finished
```{r}
rm(list=ls())
gc()
```

# bitscore blastn vs tblastx
```{r}
blastn=readRDS("./results_blastn.rds")
tblastx=readRDS("./results_tblastx.rds")
```

# Subsetting and merging data
```{r}
# Relative bitscore
max(blastn$V12)
# [1] 579
blastn$bit = blastn$V12/579*100

max(tblastx$V12)
# [1] 273
tblastx$bit = tblastx$V12/273*100

blastn_pid = blastn[,c(1,3,19)]
tblastx_pid = tblastx[,c(1,3,19)]

global_pid = inner_join(blastn_pid, tblastx_pid, by="V1")
head(global_pid)
names(global_pid) = c("otu_id", "blast_pid", "blast_bitrel", "tblastx_pid", "tblastx_bitrel")
head(global_pid)
```

# Bit relative
## Normality test Bit relative
```{r}
ks.test(global_pid$blast_bitrel, 'pnorm')
ks.test(global_pid$tblastx_bitrel, 'pnorm')
```
## bitrel wilcox test blastn vs tblastx
```{r}
paste0("median tblastx: ",  round(median(global_pid$tblastx_bitrel), 2), ", ", 
      "min: ", round(min(global_pid$tblastx_bitrel),2), ", ", 
      "max: ", round(max(global_pid$tblastx_bitrel),2))

paste("median blastn: ",  round(median(global_pid$blast_bitrel), 2), ", ", 
      "min: ", round(min(global_pid$blast_bitrel),2), ", ", 
      "max: ", round(max(global_pid$blast_bitrel),2))

paste("mean tblastx:", round(mean(global_pid$tblastx_bitrel),2), "+/-", round(sd(global_pid$tblastx_bitrel),2))
paste("mean blastn:", round(mean(global_pid$blast_bitrel),2), "+/-", round(sd(global_pid$blast_bitrel),2))

# is tblastx bit relative is greater than blastn bitrel
wilcox.test(global_pid$tblastx_bitrel, global_pid$blast_bitrel, paired = TRUE, alt="greater") # yes
```
**Notes: The relative bitscore tblastx is significantly greater than blastn**

# Pident blastn vs tbalstx
```{r}
ks.test(global_pid$blast_pid, 'pnorm')
ks.test(global_pid$tblastx_pid, 'pnorm')
```

## pidentrel wilcox test blastn vs tblastx
```{r}
paste0("median tblastx: ",  round(median(global_pid$tblastx_pid), 2), ", ", 
      "min: ", round(min(global_pid$tblastx_pid),2), ", ", 
      "max: ", round(max(global_pid$tblastx_pid),2))

paste("median blastn: ",  round(median(global_pid$blast_pid), 2), ", ", 
      "min: ", round(min(global_pid$blast_pid),2), ", ", 
      "max: ", round(max(global_pid$blast_pid),2))

paste("mean tblastx:", round(mean(global_pid$tblastx_pid),2), "+/-", round(sd(global_pid$tblastx_pid),2))
paste("mean blastn:", round(mean(global_pid$blast_pid),2), "+/-", round(sd(global_pid$blast_bitrel),2))

# is tblastx bit relative is greater than blastn bitrel
wilcox.test(global_pid$tblastx_pid, global_pid$blast_pid, paired = TRUE, alt="greater") # yes
```

# Session info
```{r}
sessioninfo::session_info(pkgs="attached")
```