---
title: "Figure 3 Blastn300 Venn"
output:
  html_notebook:
    code_folding: show
    df_print: paged
    fig_retina: 1
    fig_width: 12
    fig_height: 8
    fig_caption: yes
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: no
---

```{css, echo=FALSE}
.scroll-200 {
  max-height: 200px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{css, echo=FALSE}
.tocify .tocify-header {
  #position: fixed;
  #top: 50px;
  #left: 50px;
  width: 350px;
  #height: 400px;
  }
```

```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(reshape2)
  library(Biostrings)
  library(ggpubr)
  library(VennDiagram)
  library(gridExtra)
  })
```


# clean workspace
```{r}
rm(list=ls())
gc()
```

# results blastn / tblastx db5_results3
## remove taxaNAs blast
### nospNAs
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V18 == "s:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V18 == "s:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V18 == "s:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V18 == "s:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V18 == "s:") %>% nrow()

blst_global = blst_global %>% filter(!V18 == "s:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]
# temp = inner_join(blst_mydb, blst_imdb, by="V1")
# temp2 = inner_join(temp, blst_global, by="V1")
# blst_otus = temp2$V1
# rm(temp, temp2)
blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                "V18.loc"=blst_mydb2$V18, 
                 # regional
                 "V18.reg"=blst_imdb2$V18, 
                 # global
                 "V18.glo"=blst_global2$V18)
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$sp = top$V18.loc == top$V18.reg & top$V18.reg == top$V18.glo
```

#### VD nospNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
# venn.sp <- draw.triple.venn(
#   area1 = dim(blst_mydb2)[1], # local
#   area2 = dim(blst_imdb2)[1], # regional
#   area3 = dim(blst_global2)[1], # global
#   n12 = length(which(top$V18.loc == top$V18.reg)),
#   n23 = length(which(top$V18.reg == top$V18.glo)),
#   n13 = length(which(top$V18.loc == top$V18.glo)),
#   n123 = length(which(top$sp == TRUE)),
#   fill = c("#fbada7", "#66d688", "#a0c4ff"),
#   lty = "blank",
#   cex = 3.5,
#   cat.cex = 3, cat.default.pos = "outer", 
#   cat.pos = c(-27, 27, 135),
#   cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
# )
# p_sp = grid.arrange(gTree(children = venn.sp), bottom =textGrob("Species", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))
# 
# paste0("species: ", nrow(top)," OTUs", "; ",round(length(which(top$sp == TRUE))/nrow(top)*100,2),"%")
```

#### VD nospNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.sp <- draw.triple.venn(
  area1 = dim(blst_mydb)[1], # local
  area2 = dim(blst_imdb)[1], # regional
  area3 = dim(blst_global)[1], # global
  n12 = length(which(top$V18.loc == top$V18.reg)),
  n23 = length(which(top$V18.reg == top$V18.glo)),
  n13 = length(which(top$V18.loc == top$V18.glo)),
  n123 = length(which(top$sp == TRUE)),
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_sp = grid.arrange(gTree(children = venn.sp), bottom =textGrob("Species", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("species: ", nrow(top)," OTUs", "; ",round(length(which(top$sp == TRUE))/nrow(top)*100,2),"%")
```


### nogeNAs
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V17 == "g:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V17 == "g:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V17 == "g:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V17 == "g:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V17 == "g:") %>% nrow()

blst_global = blst_global %>% filter(!V17 == "g:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]
blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                 "V17.loc"=blst_mydb2$V17, 
                  # regional
                "V17.reg"=blst_imdb2$V17, 
                 # global
                 "V17.glo"=blst_global2$V17) 
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$ge = top$V17.loc == top$V17.reg & top$V17.reg == top$V17.glo
```

#### VD nogeNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
# venn.ge <- draw.triple.venn(
#   area1 = dim(blst_mydb2)[1], # local
#   area2 = dim(blst_imdb2)[1], # regional
#   area3 = dim(blst_global2)[1], # global
#   n12 = length(which(top$V17.loc == top$V17.reg)), #12
#   n23 = length(which(top$V17.reg == top$V17.glo)), #23
#   n13 = length(which(top$V17.loc == top$V17.glo)), #13
#   n123 = length(which(top$ge == TRUE)), #n123
#   fill = c("#fbada7", "#66d688", "#a0c4ff"),
#   lty = "blank",
#   cex = 3.5,
#   cat.cex = 3, cat.default.pos = "outer", 
#   cat.pos = c(-27, 27, 135),
#   cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
# )
# p_ge = grid.arrange(gTree(children = venn.ge), bottom =textGrob("Genus", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))
# 
# paste0("genus: ", nrow(top)," OTUs", "; ",round(length(which(top$ge == TRUE))/nrow(top)*100,2),"%")
```

#### VD nogeNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.ge <- draw.triple.venn(
  area1 = dim(blst_mydb)[1], # local
  area2 = dim(blst_imdb)[1], # regional
  area3 = dim(blst_global)[1], # global
  n12 = length(which(top$V17.loc == top$V17.reg)), #12
  n23 = length(which(top$V17.reg == top$V17.glo)), #23
  n13 = length(which(top$V17.loc == top$V17.glo)), #13
  n123 = length(which(top$ge == TRUE)), #n123
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_ge = grid.arrange(gTree(children = venn.ge), bottom =textGrob("Genus", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("genus: ", nrow(top)," OTUs", "; ",round(length(which(top$ge == TRUE))/nrow(top)*100,2),"%")
```

### nofaNAs 
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V16 == "f:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V16 == "f:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V16 == "f:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V16 == "f:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V16 == "f:") %>% nrow()

blst_global = blst_global %>% filter(!V16 == "f:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]
blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                 "V16.loc"=blst_mydb2$V16, 
                # regional
                 "V16.reg"=blst_imdb2$V16, 
                 # global
                 "V16.glo"=blst_global2$V16)
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$fa = top$V16.loc == top$V16.reg & top$V16.reg == top$V16.glo
```

#### VD nofaNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
# venn.fa <- draw.triple.venn(
#   area1 = dim(blst_mydb2)[1], # local
#   area2 = dim(blst_imdb2)[1], # regional
#   area3 = dim(blst_global2)[1], # global
#   n12 = length(which(top$V16.loc == top$V16.reg)), #12
#   n23 = length(which(top$V16.reg == top$V16.glo)), #23
#   n13 = length(which(top$V16.loc == top$V16.glo)), #13
#   n123 = length(which(top$fa == TRUE)), #n123
#   fill = c("#fbada7", "#66d688", "#a0c4ff"),
#   lty = "blank",
#   cex = 3.5,
#   cat.cex = 3, cat.default.pos = "outer", 
#   cat.pos = c(-27, 27, 135),
#   cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
# )
# p_fa = grid.arrange(gTree(children = venn.fa), bottom =textGrob("Family", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))
# 
# paste0("family: ", nrow(top)," OTUs", "; ",round(length(which(top$fa == TRUE))/nrow(top)*100,2),"%")
```

#### VD nofaNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.fa <- draw.triple.venn(
  area1 = dim(blst_mydb)[1], # local
  area2 = dim(blst_imdb)[1], # regional
  area3 = dim(blst_global)[1], # global
  n12 = length(which(top$V16.loc == top$V16.reg)), #12
  n23 = length(which(top$V16.reg == top$V16.glo)), #23
  n13 = length(which(top$V16.loc == top$V16.glo)), #13
  n123 = length(which(top$fa == TRUE)), #n123
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_fa = grid.arrange(gTree(children = venn.fa), bottom =textGrob("Family", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("family: ", nrow(top)," OTUs", "; ",round(length(which(top$fa == TRUE))/nrow(top)*100,2),"%")
```

### noorNAs 
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V15 == "o:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V15 == "o:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V15 == "o:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V15 == "o:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V15 == "o:") %>% nrow()

blst_global = blst_global %>% filter(!V15 == "o:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]
blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                 "V15.loc"=blst_mydb2$V15, 
                 # regional
                 "V15.reg"=blst_imdb2$V15, 
                # global
                 "V15.glo"=blst_global2$V15)
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$or = top$V15.loc == top$V15.reg & top$V15.reg == top$V15.glo
```

#### VD noorNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.or <- draw.triple.venn(
  area1 = dim(blst_mydb2)[1], # local
  area2 = dim(blst_imdb2)[1], # regional
  area3 = dim(blst_global2)[1], # global
  n12 = length(which(top$V15.loc == top$V15.reg)), #12
  n23 = length(which(top$V15.reg == top$V15.glo)), #23
  n13 = length(which(top$V15.loc == top$V15.glo)), #13
  n123 = length(which(top$or == TRUE)), #n123
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_or = grid.arrange(gTree(children = venn.or), bottom =textGrob("Order", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("order: ", nrow(top)," OTUs", "; ",round(length(which(top$or == TRUE))/nrow(top)*100,2),"%")
```

#### VD noorNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
# venn.or <- draw.triple.venn(
#   area1 = dim(blst_mydb)[1], # local
#   area2 = dim(blst_imdb)[1], # regional
#   area3 = dim(blst_global)[1], # global
#   n12 = length(which(top$V15.loc == top$V15.reg)), #12
#   n23 = length(which(top$V15.reg == top$V15.glo)), #23
#   n13 = length(which(top$V15.loc == top$V15.glo)), #13
#   n123 = length(which(top$or == TRUE)), #n123
#   fill = c("#fbada7", "#66d688", "#a0c4ff"),
#   lty = "blank",
#   cex = 3.5,
#   cat.cex = 3, cat.default.pos = "outer", 
#   cat.pos = c(-27, 27, 135),
#   cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
# )
# p_or = grid.arrange(gTree(children = venn.or), bottom =textGrob("Order", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))
# 
# paste0("order: ", nrow(top)," OTUs", "; ",round(length(which(top$or == TRUE))/nrow(top)*100,2),"%")
```

### VD merged noNAs
```{r, fig.showtext=TRUE, fig.width=48, fig.height=13}
# venn_blastn =  grid.arrange(arrangeGrob(p_or, p_fa, p_ge, p_sp, ncol = 4, nrow = 1), # First row with 3 plots in 3 different columns
#              # arrangeGrob(p4,p5, ncol = 2),    # Second row with 2 plots in 2 different columns
#              # arrangeGrob(p6,p7, ncol = 2),    # Third row with 2 plots in 2 different columns
#              # arrangeGrob(p_or, p_fa, p_ge, p_sp, ncol = 4, nrow = 1), 
#              # arrangeGrob(lg),  heights = c(4,4,1),                        # Number of rows
#              top = textGrob("blastn", gp=gpar(cex=5, fontfamily="Calibri", fontface="bold"),x=0.05, y= -0.25)
#              # rectGrob(gp=gpar(lwd=10, col = "red", fill=NA)))
#              )

# gb <- rectGrob(height = .98, width = .98, gp = gpar(lwd = 2, col = "red", fill = NA))
# gb = rectGrob(gp=gpar(lwd=2, col = "red", fill=NA))
# gb = rectGrob(gp=gpar(lwd=4, col = "black", fill=NA))
# 
# venn_blastn = grid.arrange(gTree(children = gList(venn_blastn, gb)))

# venn_blastn = grid.arrange(gtable::gtable_add_grob(
#   arrangeGrob(p_or, p_fa, p_ge, p_sp, ncol = 4, nrow = 1),
#                                                    rectGrob(gp=gpar(lwd=10, col = "red", fill=NA)), 1, 1, 1, 4),
#                            top = textGrob("blastn", gp=gpar(cex=5, fontfamily="Calibri", fontface="bold"),x=0.05, y= -0.2)
#                            )


# venn_blastn_blue = grid.arrange(gtable::gtable_add_grob(arrangeGrob(venn_blastn),
#                                      rectGrob(gp=gpar(lwd=10, col = "red", fill=NA)), 1, 1, 1, 1))
```

```{r, fig.showtext=TRUE, fig.width=48, fig.height=13}
venn_blastn =  grid.arrange(arrangeGrob(p_or, p_fa, p_ge, p_sp, ncol = 4, nrow = 1), # First row with 3 plots in 3 different columns
             top = textGrob("blastn", gp=gpar(cex=4, fontfamily="Calibri", fontface="bold"),x=0.06, y= -0.25))

# gb = rectGrob(gp=gpar(lwd=4, col = "black", fill=NA))
# venn_blastn = grid.arrange(gTree(children = gList(venn_blastn, gb)))
```


```{r}
rm(list = grep("venn_blastn", ls(), value=TRUE, invert = TRUE))
```

## remove taxaNAs tblastx
### nospNAs
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/tblastx.db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V18 == "s:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V18 == "s:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/tblastx.db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V18 == "s:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V18 == "s:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/tblastx.db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V18 == "s:") %>% nrow()

blst_global = blst_global %>% filter(!V18 == "s:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]

blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                "V18.loc"=blst_mydb2$V18, 
                 # regional
                 "V18.reg"=blst_imdb2$V18, 
                 # global
                 "V18.glo"=blst_global2$V18)
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$sp = top$V18.loc == top$V18.reg & top$V18.reg == top$V18.glo
```

#### VD nospNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.sp <- draw.triple.venn(
  area1 = dim(blst_mydb)[1], # local
  area2 = dim(blst_imdb)[1], # regional
  area3 = dim(blst_global)[1], # global
  n12 = length(which(top$V18.loc == top$V18.reg)),
  n23 = length(which(top$V18.reg == top$V18.glo)),
  n13 = length(which(top$V18.loc == top$V18.glo)),
  n123 = length(which(top$sp == TRUE)),
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_sp = grid.arrange(gTree(children = venn.sp), bottom =textGrob("Species", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("species: ", nrow(top)," OTUs", "; ",round(length(which(top$sp == TRUE))/nrow(top)*100,2),"%")
```

### nogeNAs
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/tblastx.db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V17 == "g:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V17 == "g:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/tblastx.db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V17 == "g:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V17 == "g:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/tblastx.db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V17 == "g:") %>% nrow()

blst_global = blst_global %>% filter(!V17 == "g:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]
blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                 "V17.loc"=blst_mydb2$V17, 
                  # regional
                "V17.reg"=blst_imdb2$V17, 
                 # global
                 "V17.glo"=blst_global2$V17) 
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$ge = top$V17.loc == top$V17.reg & top$V17.reg == top$V17.glo
```

#### VD nogeNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.ge <- draw.triple.venn(
  area1 = dim(blst_mydb)[1], # local
  area2 = dim(blst_imdb)[1], # regional
  area3 = dim(blst_global)[1], # global
  n12 = length(which(top$V17.loc == top$V17.reg)), #12
  n23 = length(which(top$V17.reg == top$V17.glo)), #23
  n13 = length(which(top$V17.loc == top$V17.glo)), #13
  n123 = length(which(top$ge == TRUE)), #n123
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_ge = grid.arrange(gTree(children = venn.ge), bottom =textGrob("Genus", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("genus: ", nrow(top)," OTUs", "; ",round(length(which(top$ge == TRUE))/nrow(top)*100,2),"%")
```


### nofaNAs 
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/tblastx.db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V16 == "f:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V16 == "f:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/tblastx.db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V16 == "f:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V16 == "f:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/tblastx.db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V16 == "f:") %>% nrow()

blst_global = blst_global %>% filter(!V16 == "f:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]
blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                 "V16.loc"=blst_mydb2$V16, 
                # regional
                 "V16.reg"=blst_imdb2$V16, 
                 # global
                 "V16.glo"=blst_global2$V16)
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$fa = top$V16.loc == top$V16.reg & top$V16.reg == top$V16.glo
```

#### VD nofaNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.fa <- draw.triple.venn(
  area1 = dim(blst_mydb)[1], # local
  area2 = dim(blst_imdb)[1], # regional
  area3 = dim(blst_global)[1], # global
  n12 = length(which(top$V16.loc == top$V16.reg)), #12
  n23 = length(which(top$V16.reg == top$V16.glo)), #23
  n13 = length(which(top$V16.loc == top$V16.glo)), #13
  n123 = length(which(top$fa == TRUE)), #n123
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_fa = grid.arrange(gTree(children = venn.fa), bottom =textGrob("Family", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("family: ", nrow(top)," OTUs", "; ",round(length(which(top$fa == TRUE))/nrow(top)*100,2),"%")
```

### noorNAs 
#### import files
```{r}
blst_mydb = read.table("./blast_db_results/tblastx.db5.local.out.top")
nrow(blst_mydb)
blst_mydb %>% filter(!V15 == "o:") %>% nrow()

blst_mydb = blst_mydb %>% filter(!V15 == "o:")
blst_mydb = blst_mydb[order(blst_mydb$V1), ]
dim(blst_mydb)
```

```{r}
blst_imdb = read.table("./blast_db_results/tblastx.db5.regional.out.top")
nrow(blst_imdb)
blst_imdb %>% filter(!V15 == "o:") %>% nrow()

blst_imdb = blst_imdb %>% filter(!V15 == "o:")
blst_imdb = blst_imdb[order(blst_imdb$V1), ]
dim(blst_imdb)
```

```{r}
blst_global = read.table("./blast_db_results/tblastx.db5.global.out.top")
nrow(blst_global)
blst_global %>% filter(!V15 == "o:") %>% nrow()

blst_global = blst_global %>% filter(!V15 == "o:")
blst_global = blst_global[order(blst_global$V1), ]
dim(blst_global)
```

```{r}
dim(blst_mydb)[1] ; dim(blst_imdb)[1] ; dim(blst_global)[1]

blst_otus = Reduce(intersect, list(blst_mydb$V1, blst_imdb$V1, blst_global$V1))

blst_mydb2 = subset(blst_mydb, V1 %in% blst_otus )
blst_imdb2 = subset(blst_imdb, V1 %in% blst_otus)
blst_global2 = subset(blst_global, V1 %in% blst_otus)

dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]
```

#### Prepare dataframe
```{r}
top = data.frame("otus"=blst_mydb2$V1, 
                 # local
                 "V15.loc"=blst_mydb2$V15, 
                 # regional
                 "V15.reg"=blst_imdb2$V15, 
                # global
                 "V15.glo"=blst_global2$V15)
dim(blst_mydb2)[1] ; dim(blst_imdb2)[1] ; dim(blst_global2)[1]

top$or = top$V15.loc == top$V15.reg & top$V15.reg == top$V15.glo
```

#### VD noorNAs
```{r, fig.showtext=TRUE, fig.width=12, fig.height=12}
venn.or <- draw.triple.venn(
  area1 = dim(blst_mydb)[1], # local
  area2 = dim(blst_imdb)[1], # regional
  area3 = dim(blst_global)[1], # global
  n12 = length(which(top$V15.loc == top$V15.reg)), #12
  n23 = length(which(top$V15.reg == top$V15.glo)), #23
  n13 = length(which(top$V15.loc == top$V15.glo)), #13
  n123 = length(which(top$or == TRUE)), #n123
  fill = c("#fbada7", "#66d688", "#a0c4ff"),
  lty = "blank",
  cex = 3.5,
  cat.cex = 3, cat.default.pos = "outer", 
  cat.pos = c(-27, 27, 135),
  cat.dist = c(0.055, 0.055, 0.055), cat.fontfamily = "Calibri"
)
p_or = grid.arrange(gTree(children = venn.or), bottom =textGrob("Order", gp=gpar(cex=3.5, fontfamily="Calibri", fontface="bold"), y= 1))

paste0("order: ", nrow(top)," OTUs", "; ",round(length(which(top$or == TRUE))/nrow(top)*100,2),"%")
```

### VD merged noNAs
```{r, fig.showtext=TRUE, fig.width=48, fig.height=16}
venn_tblastx =  grid.arrange(arrangeGrob(p_or, p_fa, p_ge, p_sp, ncol = 4, nrow = 1), # First row with 3 plots in 3 different columns
                             top = textGrob("tblastx", gp=gpar(cex=4, fontfamily="Calibri", fontface="bold"), x=0.07, y= -0.25))
lg <- legendGrob(nrow=1, ncol= 6, 
                 labels=c("Databases :", "Local", "Regional", "Global"), 
                 pch = c(0,19,19,19), hgap = 4, byrow=FALSE,
                 gp=gpar(col=c("white", "#fbada7", "#66d688", "#a0c4ff"), cex=4.5, fontfamily="Calibri", fontface="bold"))

venn_tblastx = grid.arrange(arrangeGrob(venn_tblastx, nrow = 1), # First row with 3 plots in 3 different columns
                            arrangeGrob(lg),  
                            heights = c(4,1))

# gb = rectGrob(gp=gpar(lwd=4, col = "black", fill=NA))
# 
# venn_tblastx = grid.arrange(gTree(children = gList(venn_tblastx, gb)))
```

## VD merged blastn tblastx
```{r, fig.showtext=TRUE, fig.width=48, fig.height=29}
grid.arrange(arrangeGrob(venn_blastn, nrow = 1), # First row with 3 plots in 3 different columns
             arrangeGrob(venn_tblastx, nrow = 1),    # Second row with 2 plots in 2 different columns
             # arrangeGrob(lg),
             heights = c(0.448,0.552))
             
tiff(filename = "./figures/figure3.tiff", width = 48, height = 29, units = "in", pointsize = 18, compression = "lzw", res=600)
grid.arrange(arrangeGrob(venn_blastn, nrow = 1),    # First row with 3 plots in 3 different columns
             arrangeGrob(venn_tblastx, nrow = 1),   # Second row with 2 plots in 2 different columns
             heights = c(0.43,0.57))                # Number of rows
             
dev.off()
```
