---
title: "Zizka cutadatp_subsample"
output:
  html_notebook:
    code_folding: show
    df_print: paged
    fig_width: 12
    fig_height: 8
    fig_caption: yes
    toc: yes
    toc_depth: 6
    toc_float:
      collapsed: no
---

```{css, echo=FALSE}
.scroll-200 {
  max-height: 200px;
  overflow-y: auto;
  background-color: inherit;
}
```

```{css, echo=FALSE}
.tocify .tocify-header {
  #position: fixed;
  #top: 50px;
  #left: 50px;
  width: 350px;
  #height: 400px;
  }
```

```{r}
suppressPackageStartupMessages({
  library(tidyverse) ; library(reshape2) ; library(Biostrings) ; library(phyloseq); library(iNEXT) ; library(ggpubr)
})
```

#Import otu table
```{r, fig.width=12, fig.height=8}
otu = read.table("./output/otus_finalize/otutab.300.txt", row.names = 1)
length(which(colSums(otu) < 10000))/ncol(otu)

dim(otu)
```
**180 samples and 4,505 otus**

# Using Shell Terminal
```{bash}
grep "^#" ./output/otus_finalize/otutab.300.txt > temp_colnames
sed -E 's/#OTU ID\t//' temp_colnames > temp_colnames2
### Using Shell Terminal ===
```

```{r}
temp_colnames = read.table("temp_colnames2")
dim(temp_colnames)
head(temp_colnames)
length(colnames(otu))

colnames(otu)= temp_colnames[1,]
head(otu)
```

# Meta
```{r}
meta = read.table("./metadata")
head(meta)
meta = meta[,-7]
colnames(meta) = c("Biosample", "library_name", "Submitter_acc", "Experiment_acc", "Sample_acc", "Run_acc", "Platform")

rownames(meta) = meta$Run_acc
head(meta)
meta$lib_name = paste0(str_sub(meta$library_name,1,4), str_sub(meta$library_name,-2))
```

# Refseq nonumts
```{r}
ref_seq = Biostrings::readDNAStringSet("./output/otus_finalize/otus97.final.300.nonumts.fa")
ref_seq
range(ref_seq@ranges@width)
```

# merge into  Phyloseq
```{r}
# We need to convert taxa_blast and otu to phyloseq objects to phyloseq object (matrix) before merging
otu2 = otu_table(as.matrix(otu), taxa_are_rows = T)

dim(meta)
dim(otu2)

length(ref_seq@ranges@group)

otu_phy = merge_phyloseq(otu2, ref_seq, sample_data(meta))
otu_phy

# check if otu is correct
length(intersect(rownames(otu_table(otu_phy)), rownames(otu)))
```

**important: since otu object wast 3247otus now after the merge with nonumts refseq become 3058, we need to remove the initial otu object**
```{r}
rm(otu)
```

# STOP 1
**We have created phyloseq object **

# Calculate estimateD
Rarefy the subsamples with the lowest coverage of subsample of a sample

**Use this one for calculate "estimateD"**
```{r}
library(doParallel)
cl <- makeCluster(20)  # 20 on hpcc
registerDoParallel(cl)

est <- function(TK_sample){
  require(iNEXT)
  require(tidyverse)
  require(phyloseq)
  a = data.frame(otu_table(otu_phy))
  b = data.frame(sample_data(otu_phy)) %>% subset(lib_name == TK_sample) %>% select(library_name, Run_acc) # TK_Sample == lib_name not library_name
  b = b[order(b$library_name),]
  a = a %>% select(all_of(b$Run_acc))
  c = estimateD(a, datatype="abundance", base="coverage", level=NULL, conf=0.95) 
  return(c)
}

temp = unique(meta$lib_name)
system.time(est_otu_all <- foreach(i=temp) %dopar% est(i)) # another way
stopCluster(cl)
rm(cl)
```


```{r}
est_otu_all2 = as.data.frame(do.call(rbind, est_otu_all))
est_otu_all2 = est_otu_all2 %>% filter(order == 0)
est_otu_all2
```

# Subsample otu (otu original) 
**Using SRS package & minum coverage within a sample**
```{r}
temp = est_otu_all2$m # get the number of abundance of each subsample that has same coverage across each sample (rdept)
names(temp) = est_otu_all2$site

tmp_otu = as.data.frame(otu_table(otu_phy))[,-c(1:180)] # create empty otu_table as the original otu_table

for (i in 1:length(temp)){
  a = names(temp[i])
  rdepth = temp[[i]]
  tmp = as.data.frame(otu_table(otu_phy)) %>% select(all_of(a))
  # names = row.names(tmp)
  tmp = SRS::SRS(tmp, Cmin = rdepth, set_seed = T, seed = 42) # SRS::SRS
  tmp_otu = cbind(tmp_otu, tmp)
}
head(tmp_otu)
identical(colSums(tmp_otu), temp)
```

# Create new phyloseq object
```{r}
tmp_otu2 = otu_table(as.matrix(tmp_otu), taxa_are_rows = T)
identical(colSums(tmp_otu), colSums(tmp_otu2))
srs_otu_phy = merge_phyloseq(tmp_otu2, ref_seq, sample_data(meta))

# check if it is identical
identical(colnames(otu_table(srs_otu_phy)), colnames(tmp_otu2))
identical(colSums(otu_table(srs_otu_phy)), colSums(tmp_otu2))
```

# Using Subsample "srs_otu_phy"
## Raref OTU SRS
```{r, fig.width=12, fig.height=8}
temp = unique(meta$lib_name)

srs_otu_list = list()
temp
for (i in rev(temp)){
  a = subset(sample_data(srs_otu_phy), subset = lib_name %in% i) # change the the phyloseq object (srs_otu_phy)
  b = a$Run_acc # change to correct unique sample name in otu table
  c = as.data.frame(otu_table(srs_otu_phy))[,b] # change to correc otu_table
  c[c>0]=1
  srs_otu_list = c(list(c), srs_otu_list)
}
rm(a, b, c, i)
names(srs_otu_list) = temp

ine <- function(list_name){
  require(iNEXT)
  require(tidyverse)
  require(phyloseq)
  a = srs_otu_list[list_name] # need to change to correct list object name
  b = iNEXT(a, q=c(0,1,2), datatype="incidence_raw", nboot = 100) 
  return(b)
}

library(doParallel)
ncores <- detectCores(logical=F) # physical cores
ncores = 20
cl <- makeCluster(ncores)
registerDoParallel(cl)


temp2 = list ("Lat1dL", "Lat1dS", "Lat1wL", "Lat1wS", "Lat2dL", "Lat2dS", "Lat2wL", "Lat2wS", "Lat3dL", "Lat3dS", "Lat3wL", "Lat3wS", "Lat4dL", "Lat4dS", "Lat4wL", "Lat4wS", "Lat6dL", "Lat6dS", "Lat6wL", "Lat6wS")
system.time(srs_otu_list_ine <- foreach(i=temp2) %dopar% ine(i))
stopCluster(cl)
```

```{r}
# converting the otu_list_ine become one list
ine.list = function(ine_all){
  ine_all2 = ine_all[[1]]
    for(x in 2:length(ine_all)){
    ine_all2$DataInfo = rbind(ine_all2$DataInfo, ine_all[[x]]$DataInfo)
    ine_all2$AsyEst = rbind(ine_all2$AsyEst, ine_all[[x]]$AsyEst)
    ine_all2$iNextEst = c(ine_all2$iNextEst, ine_all[[x]]$iNextEst)
  }
    return(ine_all2)
}

srs_otu_list_ine_out = ine.list(srs_otu_list_ine)
```

## Plotting
```{r,fig.width=28, fig.height=8, error=FALSE}
po1 = ggiNEXT(srs_otu_list_ine_out, facet.var = "order", type=1) + theme_bw(base_size=25) +
  ylab("OTU") + xlab("Number of subsamples") +
  scale_x_continuous(breaks = seq(0, 18, by = 1)) +
  # scale_y_continuous(breaks = seq(0, 25000, by = 5000)) +
  theme(legend.position="none", axis.text.x = element_text(size=rel(0.6), angle=35, hjust=0.5, vjust=0.8),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.border = element_rect(colour = "black", fill=NA))


po2 = ggiNEXT(srs_otu_list_ine_out, type=2) + theme_bw(base_size=25) + xlab("Number of subsamples") +
  # scale_x_continuous(breaks = seq(0, 18, by = 1)) +
  # scale_y_continuous(breaks = seq(0, 1, by = 0.05)) +
  theme(#legend.position = c(0.8,0.42),
        legend.text = element_text(size =18),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(size=rel(0.6), angle=35, hjust=0.5, vjust=0.8),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.border = element_blank(), panel.background = element_blank()) +
  geom_vline(xintercept = 4, color = "blue", linetype= "dashed", size=1.2)

po3 = ggarrange(po1, po2, nrow = 1, widths = c(0.6, 0.4))
po3
# save tiff
tiff(filename = "./output/inext_zizka_subsample_reads.tiff", width = 28, height = 8, units = "in", pointsize = 25, compression = "lzw", res=600)
plot(po3)
dev.off()
```


## Compare size & coverage
### level 0.95
```{r}
# estimateD wrapper for incidence_raw present absent
est2 <- function(TK_sample){
  require(iNEXT)
  require(tidyverse)
  require(phyloseq)
  a = srs_otu_list[TK_sample] # need to rename as chang the list object
  b = estimateD(a, datatype="incidence_raw", base="coverage", level=0.95, conf=0.95)
  return(b)
}

library(doParallel)
ncores <- detectCores(logical=F) # physical cores
ncores = 20
cl <- makeCluster(ncores)
registerDoParallel(cl)

temp = sort(unique(meta$lib_name))

system.time(srs_est2_result95 <- foreach(i=temp) %dopar% est2(i)) # another way
stopCluster(cl)

srs_est2_result95_v2 = as.data.frame(do.call(rbind, srs_est2_result95))
srs_est2_result95_v2 %>% filter(order == 0) %>% arrange(site)
```

### level 0.90
```{r}
# estimateD wrapper for incidence_raw present absent
est2 <- function(TK_sample){
  require(iNEXT)
  require(tidyverse)
  require(phyloseq)
  a = srs_otu_list[TK_sample] # need to rename as chang the list object
  b = estimateD(a, datatype="incidence_raw", base="coverage", level=0.90, conf=0.95)
  return(b)
}

library(doParallel)
ncores <- detectCores(logical=F) # physical cores
ncores = 20
cl <- makeCluster(ncores)
registerDoParallel(cl)

temp = sort(unique(meta$lib_name))

system.time(srs_est2_result90 <- foreach(i=temp) %dopar% est2(i)) # another way
stopCluster(cl)

srs_est2_result90_v2 = as.data.frame(do.call(rbind, srs_est2_result90 ))
srs_est2_result90_v2 %>% filter(order == 0) %>% arrange(site)
```

### size 4
```{r}
est2 <- function(TK_sample){
  require(iNEXT)
  require(tidyverse)
  require(phyloseq)
  a = srs_otu_list[TK_sample] # need to rename as chang the list object
  b = estimateD(a, datatype="incidence_raw", base="size", level=4, conf=0.95) # change the level appropriately
  return(b)
}

library(doParallel)
ncores <- detectCores(logical=F) # physical cores
ncores = 20
cl <- makeCluster(ncores)
registerDoParallel(cl)

temp = sort(unique(meta$lib_name))
system.time(srs_est_otu_size4 <- foreach(i=temp) %dopar% est2(i))
stopCluster(cl)

srs_est_otu_size4_v2 = as.data.frame(do.call(rbind, srs_est_otu_size4))
srs_est_otu_size4_v2 %>% filter(order == 0) %>% arrange(site)
```

```{r}
srs_est_otu_size4_v2_SC = srs_est_otu_size4_v2 %>% filter(order == 0) %>% arrange(site)
mean(srs_est_otu_size4_v2_SC$SC)
sd(srs_est_otu_size4_v2_SC$SC)
```

### size 3
```{r}
est2 <- function(TK_sample){
  require(iNEXT)
  require(tidyverse)
  require(phyloseq)
  a = srs_otu_list[TK_sample] # need to rename as chang the list object
  b = estimateD(a, datatype="incidence_raw", base="size", level=3, conf=0.95) # change the level appropriately
  return(b)
}

library(doParallel)
ncores <- detectCores(logical=F) # physical cores
ncores = 20
cl <- makeCluster(ncores)
registerDoParallel(cl)

temp = sort(unique(meta$lib_name))
system.time(srs_est_otu_size3 <- foreach(i=temp) %dopar% est2(i))
stopCluster(cl)

srs_est_otu_size3_v2 = as.data.frame(do.call(rbind, srs_est_otu_size3))
srs_est_otu_size3_v2 %>% filter(order == 0) %>% arrange(site)
```

```{r}
srs_est_otu_size3_v2_SC = srs_est_otu_size3_v2 %>% filter(order == 0) %>% arrange(site)
mean(srs_est_otu_size3_v2_SC$SC)
sd(srs_est_otu_size3_v2_SC$SC)
```

### size 9
```{r}
est2 <- function(TK_sample){
  require(iNEXT)
  require(tidyverse)
  require(phyloseq)
  a = srs_otu_list[TK_sample] # need to rename as chang the list object
  b = estimateD(a, datatype="incidence_raw", base="size", level=9, conf=0.95) # change the level appropriately
  return(b)
}

library(doParallel)
ncores <- detectCores(logical=F) # physical cores
ncores = 20
cl <- makeCluster(ncores)
registerDoParallel(cl)

temp = sort(unique(meta$lib_name))
system.time(srs_est_otu_size9 <- foreach(i=temp) %dopar% est2(i))
stopCluster(cl)

srs_est_otu_size9_v2 = as.data.frame(do.call(rbind, srs_est_otu_size9))
srs_est_otu_size9_v2 %>% filter(order == 0) %>% arrange(site)
```


# save rdata
```{r}
save.image("./otus300.RData")
```


# Session info 
```{r}
sessioninfo::session_info(pkgs="attached")
```
